{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
added paragraph about static and dynamic analysis

>>>>

Mechanisms for controlling the information flow can be implemented either dynamic or static. The dynamic approach\footnote{
The taint mode of the programming language Perl uses this mechanism.}
labels the information with security labels and propagates these labels wherever the information is used. The static
approach\footnote{This approach is implemented in Jif for Java and Flow Caml for Caml.} analyses the program code and is
therefor far more promising, because with this approach it is possible to check all evaluation paths.
